New insights into the Weddell Sea ecosystem applying a quantitative network approach

### 2022-12-28 Manuscript/Manuscript.Rmd
Finished tidying Intro

<!-- Paragraph on unweighted and weighted networks here? -->
We should maybe write a paragraph about weighted and unweighted approaches here, where we aslo introduce the approach we used...

<!-- Insights of network science to polar ecosystems -->
> [susanne] I moved the paragraph below. it makes more sense to first talk about polar regions in genaral and then introduce the Weddell Sea.
> 
Using a network approach, different types (e.g., terrestial, lake, etc.) of food webs from various geographic locations are studied worldwide, including marine polar food webs [@Carscallen2012; @Santana2013; @Kortsch2019; @Pecuchet2022]. Some of these studies from the Arctic show how food web properties (e.g., connectance) are constrained by environmental factors such as sea ice cover and seawater temperature [@Kortsch2019; @Pecuchet2022]. In the Southern Ocean, important insights have been gained into mechanisms of energy flow, the relative importance and traits of individual species and the influence of environmental variables (e.g., sea-ice) on the structure of local food webs [@Cordone2020; @Rossi2019].
> [susanne] what do you mean here: the relative importance and traits of individual species? What important mechanisms? Can we be more specefic? Can we also be more specific about how environmental variables (e.g., sea-ice) influence the structure of local food webs in the SO?

<!-- Climate change in Weddell Sea -->
The Weddell Sea is expected to be one of the last regions of the Southern Ocean to experience the consequences of climate change due to its extensive ice cover and ocean currents [@Teschke2021] resulting in less sea surface warming compared to other areas of the Southern Ocean. Because of these environmental characteristics, the Weddell Sea may serve as a refuge for Antarctic species which depend on sea ice (e.g. krill, emperor penguin, Weddell seal) or have low heat tolerance (e.g., most notothenioid fishes) due to their adaptations to freezing tempeartures [@Griffiths2017]. While essential large-scale hydrodynamic relationships are relatively well-known for this region [@deSteur2019], information on the current distribution, abundance and sensitivity to climate change is only partially known for a few species (e.g., XXXXX) [@Houstin2022].
> [susanne]it is not clear from the text why Weddell Sea is one of the last regions of the SO to face the consequences of warming, be explicit here, how are the currents affecting the Weddell Sea?
>

<!-- Food web studies about Weddell Sea / Key species or species role -->
Overall, the complexity the Weddell Sea food web is high and consists of 488 species and 16200 predator-prey interactions[@Jacob2011]. In an attempt to better understand species role related to food web stability, Jacob et al. (2011) performed secondary extinction experiments and found that the removal of small to medium-sized, and not large, organisms caused a cascade of secondary extinctions. This findings highlighted the relative importance of predators, rather than prey, in the architecture, functioning and stability of the Weddell Sea food web, which coincides with findings from recent meta-analyses in natural complex food webs [@Brose2019; @Perkins2022]. Other investigations have considered this food web though in a meta-analysis context....[more text here, WHAT DO THESE META_ANALSYES STUDIES SHOW] [@Brose2019; @Perkins2022; @Saravia2022].

@@

<!-- Objectives -->
In this study, we aim to go beyond a purely topological (presence/absence) assessment of who eats whom in the Weddell Sea ecosystem by providing a quantitative analysis of the trophic interaction network. We aim to analyse role for the structure and stability of the food web. To achieve this, we: 1) estimated the strength for each interaction in the Weddell Sea food web, 2) characterised species role considering both weighted and unweighted properties, and 3) analysed the species’ role realted to the stability of the food web. This is the first time that the interaction strength was estimated for all the interactions mostly at the species level for the Weddell sea food web

@@

The statistical distribution that best fitted the empirical interaction strength distribution of the Weddell Sea food web was a ‘gamma’ due to the high proportion of weak interactions and the existence of a few strong interactions (Figure 3, Table S3). <!-- Gamma parameters ?? -->

@@

Our analyses show that the distribution of species interaction strength at the network level is asymmetric, i.e., the Weddell Sea food web contains many weak interactions and only a few strong ones. This finding is consistent with many previous theoretical and empirical studies [e.g. @McCann1998; @Neutel2002; @Emmerson2004; @Wootton2005; @Kortsch2021]. The asymmetric distribution of interaction strength in food webs has been interpreted as an explanation for the persistence of complex communities in nature [@Bascompte2005; @Allesina2015; @Nilsson2016]. Here we show that this pattern is also prevalent in the Weddell Sea, one of the most complex food webs to date, comprising 490 species and 16041 predator-prey interactions. This finding is in someway validating the method we used, validation of allometric methods of IS estimation not including interaction dimensionality has been performed for microcosmos of relatively few species [@Jonsson2018]. <!--This finding reinforces the call for the inclusion of IS in food web studies to understand better the ecosystem functioning, and species and whole network responses to environmental perturbations.-->

@@

```{r, out.width = "12cm", echo = FALSE, fig.cap = "Scheme of a network showing the weighted and unweighted properties we used to characterize the species of the Weddell Sea food web."}
knitr::include_graphics("Fig.2_ToyFoodWeb.jpg")
```

>>>>

@@

<!-- Paragraph on unweighted and weighted networks here? -->
We should maybe write a paragraph about weighted and unweighted approaches here, where we aslo introduce the approach we used... @Susanne could you write it?

<!-- Insights of network science to polar ecosystems -->
> [susanne] I moved the paragraph below. it makes more sense to first talk about polar regions in genaral and then introduce the Weddell Sea.
>
> [Tomás] I agree.

Using a network approach, different types (e.g., terrestial, lake, marine) of food webs from various geographic locations are studied worldwide, including marine polar food webs [@Carscallen2012; @Santana2013; @Kortsch2019; @Pecuchet2022]. Some of these studies from the Arctic show how food web properties (e.g., connectance) are constrained by environmental factors such as sea ice cover and seawater temperature [@Kortsch2019; @Pecuchet2022]. In the Southern Ocean, important insights have been gained into mechanisms of energy flow, the relative importance and traits of individual species and the influence of environmental variables (e.g., sea-ice) on the structure of local food webs [@Cordone2020; @Rossi2019]. For instance, in Potter Cove (West Antarctic Peninsula) the substratum type (i.e. hard/soft or rocks/sediments) plays a significant role in the structure and stability of the food web. In Terra Nova Bay (Ross Sea), the architecture of biodiversity was reshaped by the pulsed input of sympagic food sources following sea-ice break up, with food web simplification, decreased intraguild predation, potential disturbance propagation and increased vulnerability to biodiversity loss [@Rossi2019].
> [susanne] what do you mean here: the relative importance and traits of individual species? What important mechanisms? Can we be more specefic? Can we also be more specific about how environmental variables (e.g., sea-ice) influence the structure of local food webs in the SO?
> 
>  [Tomás] I added 2 phrases in this regard.

<!-- Climate change in Weddell Sea -->
The Weddell Sea is expected to be one of the last regions of the Southern Ocean to experience the consequences of climate change due to its extensive ice cover and ocean currents [@Teschke2021] resulting in less sea surface warming compared to other areas of the Southern Ocean. This Sea plays an important role in driving global thermohaline circulation and ventilating the global abyssal ocean because it generates a considerable part of the Antarctic Bottom Water [@Fahrbach2009]. Because of these environmental characteristics, the Weddell Sea may serve as a refuge for Antarctic species which depend on sea ice (e.g. krill, emperor penguin, Weddell seal) or have low heat tolerance (e.g., most notothenioid fishes) due to their adaptations to freezing tempeartures [@Griffiths2017]. While essential large-scale hydrodynamic relationships are relatively well-known for this region [@deSteur2019], information on the current distribution, abundance and sensitivity to climate change is only partially known for a few species (e.g., emperor penguin) [@Houstin2022].
> [susanne]it is not clear from the text why Weddell Sea is one of the last regions of the SO to face the consequences of warming, be explicit here, how are the currents affecting the Weddell Sea?
>
>[Tomás] I added 2 phrases in this regard.
>
> @learsar could you add this reference to Zotero? Fahrbach, E., Beszczynska-Möller, A., & Rohardt, G. (2009). Polar oceans-an oceanographic overview. In Biological Studies in Polar Oceans-Exploration of Life in Icy Waters, G. and H. Hempel (Eds.), Wirtschaftsverlag NW, Bremerhaven (pp. 17-36). https://epic.awi.de/id/eprint/23118/

<!-- Food web studies about Weddell Sea / Key species or species role -->
Overall, the complexity the Weddell Sea food web is high and consists of 488 species and 16200 predator-prey interactions[@Jacob2011]. In an attempt to better understand species role related to food web stability, Jacob et al. (2011) performed secondary extinction experiments and found that the removal of small to medium-sized, and not large, organisms caused a cascade of secondary extinctions. This findings highlighted the relative importance of predators, rather than prey, in the architecture, functioning and stability of the Weddell Sea food web, which coincides with findings from recent meta-analyses in natural complex food webs [@Brose2019; @Perkins2022]. Other investigations have considered this food web though in a meta-analysis context, showing that high predator-prey body-mass ratios, which create weak interactions that stabilize communities against perturbations and maintain ecosystem functioning, are found for predator groups with specific trait combinations including small vertebrates and large swimming or flying predators [@Brose2019].

> [susanne] more text here, WHAT DO THESE META_ANALSYES STUDIES SHOW [@Brose2019; @Perkins2022; @Saravia2022].
>
> [Tomás] I added specific results from Brose2019.

<!-- Objectives -->
In this study, we aim to go beyond a purely topological (presence/absence) assessment of who eats whom in the Weddell Sea ecosystem by providing a quantitative analysis of the trophic interaction network. We aim to analyse the species' role for the structure and stability of the food web. To achieve this, we: 1) estimated the strength for each interaction in the Weddell Sea food web, 2) characterised species role considering both weighted and unweighted properties, and 3) analysed the species’ role realted to the stability of the food web. This is the first time that the interaction strength was estimated for all the interactions mostly at the species level for the Weddell sea food web

@@

The statistical distribution that best fitted the empirical interaction strength distribution of the Weddell Sea food web was a ‘gamma’ due to the high proportion of weak interactions and the existence of a few strong interactions (Figure 3, Table S3). <!-- Gamma parameters ?? [Tomás] I added them in Sup Mat -->

@@

Our analyses show that the distribution of species interaction strength at the network level is asymmetric, i.e., the Weddell Sea food web contains many weak interactions and only a few strong ones. This finding is consistent with many previous theoretical and empirical studies [e.g. @McCann1998; @Neutel2002; @Emmerson2004; @Wootton2005; @Kortsch2021]. The asymmetric distribution of interaction strength in food webs has been interpreted as an explanation for the persistence of complex communities in nature [@Bascompte2005; @Allesina2015; @Nilsson2016]. Here we show that this pattern is also prevalent in the Weddell Sea, one of the most complex food webs to date, comprising 490 species and 16041 predator-prey interactions. This finding is in someway validating the method we used, validation of allometric methods of interaction strength estimation not including interaction dimensionality has been performed for microcosmos of relatively few species [@Jonsson2018]. <!--This finding reinforces the call for the inclusion of IS in food web studies to understand better the ecosystem functioning, and species and whole network responses to environmental perturbations.-->

@@

```{r, out.width = "12cm", echo = FALSE, fig.cap = "Scheme of a network showing the weighted and unweighted properties we used to characterize the species of the Weddell Sea food web. Directed arrows indicate the flow of energy; the width of the arrow represents the interaction strength of it."}
knitr::include_graphics("Fig.2_ToyFoodWeb.jpg")
```
